\documentclass[letterpaper,10pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{CormorantGaramond}
\usepackage{charter}
\usepackage{xcolor}

\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

\pagestyle{fancy}
\fancyhf{}
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}
\setlength{\footskip}{4.0pt}
\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1} \vspace{10pt}
    {\color{accentLine} \hrule} \vspace{2pt}
    \footnotesize{#2} \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\titleformat{\section}{\vspace{-5pt}\color{accentText}\raggedright\large\bfseries}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\tinysection}[1]{\phantomsection\addcontentsline{toc}{section}{#1}{\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}}
\newcommand{\headingBf}[2]{\par\noindent\hspace*{10pt}\textbf{#1}\hfill\textbf{#2}}
\newcommand{\headingIt}[2]{\par\noindent\hspace*{10pt}\textit{#1}\hfill\textit{#2}}
\newenvironment{resume_list}{\vspace{-7pt}\begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]}{\end{itemize}}
\newcommand{\itemTitle}[1]{\item[] \underline{#1}\vspace{4pt}}
\renewcommand\labelitemi{--}

\begin{document}

  \documentTitle{Randy Chan Yi Zhong}{
    \href{tel:+6596993596}{\faPhone\ +65 9699 3596} ~ | ~
    \href{mailto:randychan_92@outlook.com}{\faEnvelope\ randychan\_92@outlook.com} ~ | ~
    \href{https://linkedin.com/in/randychan112/}{\faLinkedin\ linkedin.com/in/randychan112/} ~ | ~
    \href{https://randyharrogates.github.io/my-portfolio}{\faGlobe\ randyharrogates.github.io/my-portfolio}
  }

  \tinysection{Executive Summary}
  GenAI Solutions Engineer with 7+ years of experience designing, deploying, and operating production AI systems across financial services and healthcare. Expert in Multi-Agent orchestration (LangGraph), Enterprise RAG, model serving optimization, and agentic governance. Proven ability to partner with customer stakeholders to convert AI ambition into production-ready, scalable systems through Proof-of-Concept delivery, technical enablement, and solution architecture. Skilled in bridging deep technical depth (Python, AWS, Azure, GCP, Kubernetes) with customer-facing communication to deliver trusted, high-impact GenAI solutions. ECBA-certified (IIBA) professional experienced in mentoring engineering teams and championing responsible AI practices.

  \section{Skills}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=120pt]
      \item[\textbf{Solution Engineering}] Solution Architecture, Customer Requirements Analysis, POC Delivery, Technical Demos, Solution Scoping, Technical Documentation (BPMN), Agile/Scrum, Responsible AI.
      \item[\textbf{GenAI \& LLMs}] Multi-Agent Orchestration, LangGraph, LangChain, Agentic AI, RAG Architectures, Model Fine-Tuning, LLM Evaluation (LangFuse), Prompt Engineering, NLU, Intent Classification, Human-in-the-Loop Governance, MCP.
      \item[\textbf{Model Serving}] OpenAI API, Anthropic API, Gemini API, HuggingFace Transformers, PyTorch, Token Optimization, Latency/Throughput Tuning.
      \item[\textbf{Backend}] Python (FastAPI, Flask), Java (Spring Boot), NodeJS, REST API Design, OpenAPI/Swagger.
      \item[\textbf{Data \& State}] Vector DBs (Pinecone, Weaviate), MongoDB Atlas, PostgreSQL, Redis.
      \item[\textbf{Cloud \& Infra}] AWS (ECR, ECS, S3), Azure (Container Apps, Service Bus, Blob Storage), GCP, Docker, Kubernetes, Terraform (IaC), CI/CD (GitHub Actions).
  \end{itemize}

  \section{Experience}

  \headingBf{TrustPlus AI (Fintech)}{June 2025 -- Present}
  \headingIt{Senior AI Software Engineer}{}
  \begin{resume_list}
    \itemTitle{Project: Autonomous Credit Risk \& Multi-Agent Research Suite}
    \item Architected a production-grade Multi-Agent orchestration system using LangGraph and Python, partnering with customer stakeholders to automate end-to-end credit risk assessment and brand risk management for KYB processes.
    \item Reduced total inference latency by 60 percent by designing a concurrent orchestration state layer that manages parallel tool-calling and asynchronous agentic flows, balancing model quality against throughput and token cost constraints.
    \item Implemented agentic governance controls including Human-in-the-Loop review gates for high-risk credit decisions and configurable approval workflows to ensure responsible and compliant AI operations.
    \item Led technical enablement sessions and solution demonstrations for customer stakeholders, translating complex multi-agent architectures into actionable business value propositions and adoption roadmaps.
    \item Established automated regression testing and evaluation pipelines using LLM-as-a-judge patterns to validate tool-selection precision, factual faithfulness, and detect output drift across model versions.
    \item Enhanced system observability by deploying LangFuse for end-to-end tracing, token usage analytics, and LLM performance monitoring, presenting the business case to technical and non-technical stakeholders.
    \item Optimized RAG pipelines with pre-caching, semantic-aware chunking, and optimized vector search to minimize time-to-first-token for generated credit memos and financial analysis reports.
    \item Managed the full infrastructure lifecycle using Terraform to provision Azure Service Bus, MongoDB Atlas, and cloud-native container environments, with CI/CD on GitHub Actions reducing deployment time by 40 percent.
  \end{resume_list}

  \headingBf{BGC Group}{Feb 2025 -- May 2025}
  \headingIt{Senior Software Engineer (AI Application Specialist) --- Contract}{}
  \begin{resume_list}
    \item Architected the full-stack application layer for an enterprise Task Assistant, collaborating with business users to productionize RAG workflows using FastAPI for internal knowledge management.
    \item Engineered backend middleware to orchestrate communication between the application layer and AI model endpoints, optimizing for high-concurrency handling and low-latency response times.
    \item Developed stateful session management and multi-turn conversational logic with seamless escalation to human agents, implementing Human-in-the-Loop protocols for complex user intents.
    \item Optimized retrieval precision by implementing advanced semantic-aware chunking strategies and utilizing t-SNE embedding analysis to visualize and refine document vector distributions.
    \item Integrated Weaviate (vector) and MongoDB (state) to support retrieval and storage requirements, focusing on data consistency and query performance across heterogeneous database systems.
    \item Built containerized CI/CD pipelines using Docker for reliable delivery across development, staging, and production environments.
  \end{resume_list}

  \headingBf{AI Singapore}{Jan 2024 -- Oct 2024}
  \headingIt{AI Engineer}{}
  \begin{resume_list}
    \item Mentored 12 apprentices across two cohorts in NLP and LLM techniques, developing structured curricula to accelerate skill development in modern AI engineering workflows.
    \item Designed and deployed a multi-agent RAG system for intelligent activity scheduling, leveraging LangGraph to orchestrate complex decision-making logic and autonomous tool-calling for web-scraped data retrieval.
    \item Architected an end-to-end AI pipeline for a healthcare environment in collaboration with clinical domain experts, integrating five specialized models for NER and event prediction with a focus on patient data privacy.
    \item Conducted extensive experimentation on state-of-the-art frameworks, performing hyper-parameter tuning that yielded a 50 percent increase in model performance, documenting trade-offs between model quality, latency, and compute cost.
    \item Implemented advanced RAG architectures utilizing Pinecone and sophisticated prompting techniques including few-shot prompts to maximize accuracy and reliability of generated outputs.
    \item Orchestrated containerized deployment of full-stack AI applications using FastAPI and Docker on AWS (ECR and ECS) for scalable, production-grade model serving.
    \item Championed AI explainability by implementing Explainable Boosting Machines (EBM) and interpretability frameworks, ensuring AI-driven predictions met ethical standards and transparency requirements of medical stakeholders.
  \end{resume_list}

  \headingBf{NCS Pte. Ltd.}{Oct 2022 -- Dec 2023}
  \headingIt{Business Systems Analyst (Backend Automation \& Integration)}{}
  \begin{resume_list}
    \item Engineered a Python-based automation suite to track and validate complex JSON configuration changes across distributed environments for a nation-wide healthcare web application, improving operational productivity by 50 percent.
    \item Orchestrated end-to-end data migration pipelines between SQL databases and virtualized environments, ensuring 99.9 percent data integrity for high-traffic production systems.
    \item Designed comprehensive technical documentation and system workflow diagrams (BPMN), communicating complex backend architectures to cross-functional engineering teams and advising on PDPA regulatory compliance.
  \end{resume_list}

  \headingBf{Bitopia Technology Pte. Ltd.}{Jan 2022 -- Oct 2022}
  \headingIt{Full-Stack Software Engineer}{}
  \begin{resume_list}
    \item Designed and delivered scalable RESTful microservices for logistics and real-estate platforms, leading client-facing requirements workshops to translate domain workflows into modular service architectures.
    \item Optimized PostgreSQL schemas and complex SQL queries powering real-time logistics tracking, improving dashboard response times and enabling clients to meet SLA requirements.
  \end{resume_list}

  \headingBf{Napshot Pte. Ltd.}{Jan 2019 -- Dec 2021}
  \headingIt{Solutions \& Software Engineer}{}
  \begin{resume_list}
    \item Led end-to-end solution design and delivery for SME clients across F\&B, hospitality, and HR verticals, building custom platforms (VueJS, ReactJS, Flask) and managing cloud infrastructure with 99.9 percent uptime.
    \item Conducted client requirements workshops and translated business workflows into technical specifications, serving as the primary technical point of contact for 10+ concurrent client engagements.
    \item Delivered Proof-of-Concept demonstrations and solution architecture presentations to prospective clients, scoping technical feasibility and aligning proposed solutions with business objectives and budget constraints.
  \end{resume_list}

  \section{Education \& Certifications}
  \headingBf{Singapore University of Social Sciences}{2016 -- 2022}
  \headingIt{B.Sc. in Information and Communication Technology (GPA 4.2/5) | Minor: Data Science}{}
  \begin{resume_list}
    \item \textbf{Certified Associate AI Engineer (CAIE)} - AI Professionals (AIP), Singapore.
    \item \textbf{Entry Certificate in Business Analysis (ECBA)} - IIBA.
  \end{resume_list}

\end{document}
